### 2015-01-14 publishing/plos_template.tex
added abstract form Utas final manuscript

>>>>

Recently 3D printing has emerged as a method for directly printing complete microfluidic chips, 
although printing materials have been limited to non­oxygen permeable materials.
We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D printed microfluidic devices as a means to enable oxygen control cell culture studies.
Two devices are presented and characterized.
